---
title: "LAB 10"
author: "MG"
output: pdf_document
---


## ALGORITHM

1. Import "mtcars" dataset.
2. Define a seperate function for the momentum optimizer.
3. For the function, get the number of iterations beforehand and perform the operation.
4. For each iteration, update the loss function.
5. Finally print the optimal intercept, slope and loss function.
5. Plot the data points.

## CODE

```{r}
rm(list=ls())
Mgd<-function(x1,x2,y,m1,m2,c,alpha,gamma,iter){
  iterations=0
  Lf<-0
  u_m1<-0
  u_m2<-0
  u_c<-0
  while(iterations<=iter){
    y_pred<-m1*x1+m2*x2+c
    Lf_new<-0.5*sum((y_pred-y)^2)
    nu_m1<-gamma*u_m1+alpha*sum((y_pred-y)*x1)
    nu_m2<-gamma*u_m2+alpha*sum((y_pred-y)*x2)
    nu_c<-gamma*u_c+alpha*sum(y_pred-y)
    m1<-m1-nu_m1
    m2<-m2-nu_m2
    c<-c-nu_c
    u_m1<-nu_m1
    u_m2<-nu_m2
    u_c<-nu_c
    Lf<-Lf_new
    iterations=iterations +1
  }
  return(paste("optimal intercept: ",c,"optimal slope: ",m1,m2,"Loss function: ",Lf,"iterations: ",iterations))
}
```

```{r}

data1<-mtcars
plot(data1$mpg,data1$wt,col="red",pch=20)
Mgd(data1$wt,data1$hp,data1$mpg,-0.2,-0.2,32,0.000002,0.99,20000)
lr<-lm(data1$mpg~data1$hp+data1$wt)
lr
```

## INFERENCE

The columns "wt" and "mpg" we taken as the primary datapoints and momentum optimization was applied. the optimal slope and intercept were obtained by performing momentum gradient descent on the loss funtion over given number of iterations. 