---
title: 'Ex. No 7 : Partitioning Based Clustering'
output:
  word_document: default
  pdf_document: default
  html_document:
    fig_height: 4
    highlight: pygments
    theme: spacelab
---


* * *
## Aim: Partitioning Based Clustering for USArrests Dataset

#To study and understand the following operations/functions on ‘iris’ data and perform similar operations on ‘USArrests’ dataset based on given instructions. 

#Load necessary packages using library(packagename)
```{r}
library(factoextra) 
library(cluster)
```


#Load the data
```{r}
data <- read.csv("USArrests.csv",row.names=1) 
df <- scale(data) 
```


* * *

# Algorithm:

1. Import the required libraries
2. Import the USArrests dataset
3. Scale the data accordingly
4. Remove features which are not required
5. Find the Elbow Value
5.1. Find the elbow value using for loop (
5.2. Find the elbow value using fviz_nbclust
6. Design the K Means model
7. Draw the graph of clustering(For K Means)
8. Print the parameters for k Means model
9. Design K Medoids model
10. Print the graph of clustering model (For K Medoids)
11. Print the parameters for k Medoids model

* * *
## Import libraries

```{r}
library(cluster) 
library(factoextra)
```

## Import dataset
```{r}
rm(list=ls()) ## clear env
data <- read.csv("USArrests.csv",row.names=1) ## read data and first row is the name of the features
```

## Scale the data
```{r}
df<-scale(data)
df
```


### There are two ways to find the centers for Kmeans

## Centers using for loop

```{r}
Kmax <- 15
WCSS <- rep(NA,Kmax)
nClust <- list()
for (i in 1:Kmax){
 fit<- kmeans(df,i)
 WCSS[i] <- fit$tot.withinss
 nClust[[i]] <- fit$size
}
plot(1:Kmax,WCSS,type="b")
```
## Method two using factoextra library

```{r}
fviz_nbclust(df, kmeans, method = "wss", k.max = 15)

```

## Elbow point and ploting clusters

```{r}
fit<-kmeans(df,6)
fviz_cluster(fit, df)
print(fit)
```

## Print paramenters for k means model

```{r}
print(fit$cluster)
print(fit$centers)
print(fit$withinss)
print(fit$tot.withinss)
print(fit$size)
```


## Perform K-Medoids

```{r}
fitm <- pam(df, 6, metric = "manhattan") # K-Medoids
fviz_cluster(fitm, df)
print(fitm)
```
## Print paramenters for k Medoids model

```{r}
fitm$medoids
fitm$clustering
```
* * *
## Inference and Result


We have designed and implemented a classifer for USArrests dataset.We used two methods K Means and K Medoids to classify the dataset we were able to find
clusters or the elbow point by finding the cost function for clustrs ranign from 1 to 10 and then plotting it. We then take a point where the graph starts to plateau. Here the gra[h plateaus at around value 6. We are using that to do K Means and K Medoids CLustering.

Since there is no overlap in the model so obtianed by the K Means Classifier in comparison to the K Mediods onne, which has class over in few centers.


* * *

